Fuel switch, savings, electrification - Decarbonisation in industry OR Pathways to Carbon Neutral Industrial Sectors: Integrated Modelling Approach with High Level of Detail for End-use Processes OR Decarbonization options in industry and conceptual model of industry in the integrated energy system

### 2018-01-19 article.tex
Updates from ShareLaTeX

In production, there is a high diversity of end-use while the role of gas as a fule is predominant. 
Space heating and transport dominate the total energy use in the service sector. While most space heat already supplied by district heat, natural gas is the second.

Furthermore, the data show an un-even distribution of fuel consumption in the various groups, with electricity (34\%) and gasoil/kerosene (25\%) being predominant in agriculture, electricity (31\%) and natural gas (31\%) in production, and electricity (50\%) and district heating (37\%) dominating the service sector.

\\
This preliminary description of the Danish industry poses the bases for the modelling of the sector and the investigation of decarbonisation options. Indeed, with a clear overview of the end-use processes and the related fuel consumption, the industry sector can be conveniently integrated in an energy system model. 
The following section proposes a mathematical model for the industry sector and investigates on extensions to analyse decarbonisation options.

@@

\subsection{Geographical mapping of industrial energy consumption}
District heating plays a major role in Denmark. ... \% of of space heat demand is supplied via ... district heat networks. Provided that the supply of the district will be transformed to completely renewable ones \texit{(source Maries district heat paper?)}, an increased use of district heat for space and process heat for industry is an important option to reduce fossil fuel usage. The feasibility of this option depends on the location of this industrial demand. Whether the company is located within or in vicinity to a district heating area decides whether this option can be used. Depending on the required temperature, heat pumps would be necessary to raise the provided temperature. The vicinity to such a network is furthermore decisive for the possibility of excess heat usage. Connection to a district heat network offers the possibility to exploit the otherwise lost heat potential beyond recycling it on site.

>>>>

In production, there is a high diversity of end-use while the role of gas as a fuel is predominant. 
Space heating and transport dominate the total energy use in the service sector. While most space heat already supplied by district heat, natural gas is the second.

Furthermore, the data show an un-even distribution of fuel consumption in the various groups, with electricity (34\%) and gasoil/kerosene (25\%) being predominant in agriculture, electricity (31\%) and natural gas (31\%) in production, and electricity (50\%) and district heating (37\%) dominating the service sector.
\\
This preliminary description of the Danish industry poses the bases for the modelling of the sector and the investigation of decarbonisation options. Indeed, with a clear overview of the end-use processes and the related fuel consumption, the industry sector can be conveniently integrated in an energy system model. 
The following section proposes a mathematical model for the industry sector and investigates on extensions to analyse decarbonisation options.

@@

\subsection{Geographical mapping of industrial energy consumption}
District heating plays a major role in Denmark. ... \% of of space heat demand is supplied via ... district heat networks. Provided that the supply of the district will be transformed to completely renewable ones \textit{(source Maries district heat paper?)}, an increased use of district heat for space and process heat for industry is an important option to reduce fossil fuel usage. The feasibility of this option depends on the location of this industrial demand. Whether the company is located within or in vicinity to a district heating area decides whether this option can be used. Depending on the required temperature, heat pumps would be necessary to raise the provided temperature. The vicinity to such a network is furthermore decisive for the possibility of excess heat usage. Connection to a district heat network offers the possibility to exploit the otherwise lost heat potential beyond recycling it on site.
